---
title: "Dynamic search Results"
output:
  pdf_document: default
  html_notebook: default
  html_document:
    df_print: paged
  word_document: default
---

```{r include = FALSE}
source('dyn_data_analysis.R')
library(BayesFactor)
```

## Results

### Experiment 1

#### 1.1. Correct RTs from Experiment 1

```{r fig1}
figRTs$exp1
```

#### 1.2. RT statistics

```{r exp1rt_st}
rt_anova$exp1$ANOVA
```

#### 1.3. Slopes,d' and biases:

```{r figcb1}
fig_combine$exp1
```

#### 1.4. ANOVA for the slopes

```{r}
slope_anova$exp1$ANOVA
```

The interaction in the slopes was mainly caused by the large slope in the static target-absent condition. We further tested if the slopes in the dynamic conditions were the same or not. 


first, confirmation of the original study, 'present' slopes had no difference. 
```{r}
a1 = dat$exp1$slope %>% filter(target == 'Present') %>%
  ezANOVA(data = ., dv = slope, wid = sub, within = dyn)
a1$ANOVA
```


Bayes Factor:
```{r}
dat$exp1$slope$sub <- factor(dat$exp1$slope$sub)
bf = dat$exp1$slope %>% filter(target == 'Present') %>%
  anovaBF(slope ~ dyn + sub, whichRandom = "sub", data = .)
bf
```

```{r}
a1 = dat$exp1$slope %>% filter(dyn == 'Dynamic') %>%
  ezANOVA(data = ., dv = slope, wid = sub, within = target)
a1$ANOVA
```

```{r}
bf = dat$exp1$slope %>% filter(dyn == 'Dynamic') %>%
  anovaBF(slope ~ target + sub, whichRandom = "sub", data = .)
bf
```

#### 1.5 ANOVA for d' and bias C

Search discrimination sensitivity d':
```{r}
d_anova$exp1$ANOVA
```

Search response bias C:

```{r}
c_anova$exp1$ANOVA
```

### Experiment 2

#### 2.1. Correct RTs from Experiment 2

```{r fig1}
figRTs$exp2
```

#### 2.2. RT statistics

```{r exp1rt_st}
rt_anova$exp2$ANOVA
```

#### 2.3. Slopes,d' and biases:

```{r figcb1}
fig_combine$exp2
```

#### 2.4. ANOVA for the slopes

```{r}
slope_anova$exp2$ANOVA
```

Examine if the slopes in the dynamic search differ between the target absent/present, reward present/absent. 

```{r}
a21 = dat$exp2$slope %>% filter(dyn == 'Dynamic') %>%
  ezANOVA(data = ., dv = slope, wid = sub, within = .(target,reward))
a21$ANOVA
```

#### 2.5 ANOVA for d' and bias C

Search discrimination sensitivity d':
```{r}
d_anova$exp2$ANOVA
```

Search response bias C:

```{r}
c_anova$exp2$ANOVA
```

### Experiment 3

Here is the __former Experiment 5__, with increase difficulity in the search task. 

#### 3.1. Correct RTs from Experiment 3

```{r fig1}
figRTs$exp5
```

#### 3.2. RT statistics

```{r exp3rt_st}
rt_anova$exp5$ANOVA
```

#### 3.3. Slopes,d' and biases:

```{r figcb5}
fig_combine$exp5
```

#### 3.4. ANOVA for the slopes

```{r}
slope_anova$exp5$ANOVA
```

We further test if the slope in the dynamic condition was different.

```{r}
a5 = dat$exp5$slope %>% filter(dyn == 'Dynamic') %>%
  ezANOVA(data = ., dv = slope, wid = sub, within = target)
a5$ANOVA
```

Bayes Factor:
```{r}
dat$exp5$slope$sub <- factor(dat$exp5$slope$sub)
bf = dat$exp5$slope %>% filter(dyn == 'Dynamic') %>%
  anovaBF(slope ~ target + sub, whichRandom = "sub", data = .)
bf
```


and the 'present' slopes between the dynamic and static displays
```{r}
a6 = dat$exp5$slope %>% filter(target == 'Present') %>%
  ezANOVA(data = ., dv = slope, wid = sub, within = dyn)
a6$ANOVA
```

Bayes Factor:
```{r}
bf = dat$exp5$slope %>% filter(target == 'Present') %>%
  anovaBF(slope ~ dyn + sub, whichRandom = "sub", data = .)
bf
```

#### 3.5 ANOVA for d' and bias C

Search discrimination sensitivity d':
```{r}
d_anova$exp5$ANOVA
```

Search response bias C:

```{r}
c_anova$exp5$ANOVA
```

See if the 'dynamic' search had neutral response. 

== Todo: test if the C in the dynamic conditions differ from 0 ==

